---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = TRUE
)

devtools::load_all()
```
# rtaxref – an R client to the French Taxonomical Reference

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![codecov](https://codecov.io/gh/Rekyt/rtaxref/branch/master/graph/badge.svg)](https://codecov.io/gh/Rekyt/rtaxref)
[![R-CMD-check](https://github.com/Rekyt/rtaxref/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Rekyt/rtaxref/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->



The goal of rtaxref is to provide an R client to TaxRef API, the French Taxonomical Reference and associated database on species. The API provides nomenclature, taxonomy, biogeographic repartition, statuses and interactions of species. See the API documentation [here](https://taxref.mnhn.fr/taxref-web/api/doc).


## Installation

`rtaxref` is not yet on CRAN. However, you can install the development version of `rtaxref` from GitHub with:

```r
# install.packages("remotes")
remotes::install_github("Rekyt/rtaxref")
```

## Usage

`rtaxref` contains functions to retrieve data from TaxRef-Hub. The access data is released under the [Creative Commons Attribution-ShareAlike 3.0 (CC BY-SA 30) license](https://creativecommons.org/licenses/by-sa/3.0/). A suggestion of citation is included in `rtaxref` via `citation("rtaxref")`.

To avoid collisions with other packages all `rtaxref` functions are prefixed with `rt_*()`, for example `rt_taxa_id()` lets you access to the information about a taxon using its unique id (also called `cdNom` in TaxRef):

```{r rt_taxa_id}
rtaxref::rt_taxa_id(id = 101027)
```

You get information about the taxon related to taxonomy, the referance name, vernacular names as well as distribution information.

`rt_taxa_search()` let's you search a taxon with different criteria:

```{r rt_taxa_search}
rtaxref::rt_taxa_search(sciname = "Helianthus annuus")
```

You a full list of functions included in `rtaxref` by going to the [`rtaxref` website](https://rekyt.github.io/rtaxref).

## Dependency network (Imports only)

```{r dependency_network_imports, echo=FALSE, message=FALSE, warning=FALSE}
source("https://gist.githubusercontent.com/Rekyt/261c2c3040715dcd8c211d7f5d18c9c8/raw/")
plot_dependencies()
```

## Dependency network (Imports and Suggests)

```{r dependency_network_full, echo=FALSE, message=FALSE, warning=FALSE}
source("https://gist.githubusercontent.com/Rekyt/261c2c3040715dcd8c211d7f5d18c9c8/raw/")
plot_dependencies(type = "full")
```

## Code of Conduct

Please note that the 'rtaxref' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

## Related projects

Other packages lets you work with taxonomical information from relevant databases:

- [`taxize`](https://github.com/ropensci/taxize) let's you work with many databases as well as clean a list of taxon names,
- [`ritis`](https://github.com/ropensci/ritis) a client for another taxonomic database,
- [`taxa`](https://github.com/ropensci/taxa) a package that proposes a reference class for taxonomic information (maybe used by `rtaxref` in the future),
- [CRAN taxonomy Task View](https://github.com/ropensci/taxonomy) references many related packages that are used to work with taxonomic information.
