---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)

# devtools::load_all()
```
# rtaxref – an R client to the French Taxonomical Reference

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip) [![Build Status](https://travis-ci.org/Rekyt/rtaxref.svg?branch=master)](https://travis-ci.org/Rekyt/rtaxref)

The goal of rtaxref is to provide an R client to TaxRef, the French Taxonomical Reference.

## Installation

You can install the development version of rtaxref from GitHub with:

``` r
remotes::install_github("Rekyt/rtaxref")
```

## Using `rtaxref`

For the moment `rtaxref` only contains function to interact with TaxRef on taxon's name and id.

`rt_taxa_search()` let's you search a taxon with different criteria:

```{r rt_taxa_search}
rt_taxa_search(sciname = "Helianthus annuus")
```

Other taxa functions `rt_taxa_children()`, `rt_taxa_id()`, `rt_taxa_parent()`, `rt_taxa_taxrefhistory()`, all use a single argument `id` to retrieve their data. The `id` is the unique identifier of the taxa in TaxRef and is also called `cdNom`.

```{r rt_taxa_id}
rt_taxa_id(id = 101027)
```
