---
title: "Introduction to rtaxref"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rtaxref}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rtaxref)
```

rtaxref queries [the API](https://taxref.mnhn.fr/taxref-web/api/doc) of
[the French Taxonomic Referential (TAXREF)](https://inpn.mnhn.fr/programme/referentiel-taxonomique-taxref).
This referential contains much taxonomical information as well as many other
kinds of information (occurrence in French territories, conservation statuses,
etc.).


## Searching for a taxon name

TODO explain `rt_taxa_search()`.

Talk about importance of id of species (CD_NOM).

Refer to the documentation of function to get lists of values of potential
arguments.

Querying a specific version of TAXREF.

## Retrieving the status of species


## Additional info

Vernacular names, history of taxon in TAXREF, uses


## Getting interaction data

## Linking this information to other databases

externals ids and related databases.
